\vspace{-5mm}\fontsize{22pt}{10pt}\selectfont Smoothed Analysis in Learning: Tensors and $k$-Means

### 2015-05-15 paper.tex
tensorz

$$\mbox{WC}_A(n) = \max_{x \in \Omega_n}T_A[x].$$
The \emph{smoothed complexity} of $A$ with $\sigma$-Gaussian perturbations is given by
$$\mbox{Smoothed}_A^{\sigma}(n) = \max_{\x\in [-1,1]^n}
\mathbb{E}_g[T_A(x + g)],$$ where $g$ is a Gaussian random vector of
variance $\sigma^2$. The original input $x$ is perturbed by $g$ to
obtain a new input $x + g$, which is given to the algorithm.

@@

\section{Tensor Decomposition}
Among other problems, tensor decomposition methods can be used to
learn topic models, multi-view mixture models, phylogenetic trees, and
detect communities. Tensors are especially useful in learning because
under mild conditions, the factors of a rank-$k$ 3-tensor decomposition $T =
\sum_{i=1}^ka_i \otimes b_i \otimes c_i$ are unique
\cite{tensorunique}.

>>>>

$$\mbox{WC}_A(n) = \max_{x \in \Omega_n}T_A[x].$$
The \emph{smoothed complexity} of $A$ with $\sigma$-Gaussian perturbations is given by
$$\mbox{Smoothed}_A^{\sigma}(n) = \max_{x\in [-1,1]^n}
\mathbb{E}_g[T_A(x + g)],$$ where $g$ is a Gaussian random vector of
variance $\sigma^2$. The original input $x$ is perturbed by $g$ to
obtain a new input $x + g$, which is given to the algorithm.

@@

\section{Tensor Decomposition}
(FIX): Among other problems, tensor decomposition methods can be used
to learn topic models, multi-view mixture models, phylogenetic trees,
and detect communities. Tensors are especially useful in learning
because under mild conditions, the factors of a rank-$k$ 3-tensor
decomposition $T = \sum_{i=1}^ka_i \otimes b_i \otimes c_i$ are unique
\cite{tensorunique}. These conditions extend naturally to higher-order
tensors. Assume we are given a $l$-order tensor $T$ of dimension $n$
(so $T\in \mathbb{R}^{n^{\times l}}$) and of rank $R$ and we want to
decompose it into a sum of rank-one tensors, i.e.:
$$T = \sum_{i=1}^R u_i^{(1)}\otimes u_i^{(2)}\otimes\dots\otimes
u_i^{(l)}$$ We first describe conditions under which such
decomposition is unique and computable in polynomial time.

The algorithm above works well in the \emph{exact} case, when we know
$T$. But in the learning setting, we don't know $T$ exactly--we have
an approximation $\~ T$ of $T$, since we can only take polynomially
many samples [VAGUE?]. Hence, we need to make sure the algorithm is
robust in the presence of noise. In particular, we prove that if each
entry of $E=T-\~ T$ is bounded by $\epsilon \cdot
\mbox{poly}_l(1/k,1/n,1/\delta)$, then we can compute a decomposition
in which each rank-$1$ tensor in the decomposition has an additive
error of at most $\epsilon$.
